### 2025-04-09 download-football-data.qmd
20250409 - remove implausible values

>>>>

Let's remove infinite (implausible) values:

```{r}
nfl_actualStats_seasonal_player[sapply(nfl_actualStats_seasonal_player, is.infinite)] <- NA
nfl_actualStats_seasonal_team[sapply(nfl_actualStats_seasonal_team, is.infinite)] <- NA
nfl_actualStats_seasonal_player_inclPost[sapply(nfl_actualStats_seasonal_player_inclPost, is.infinite)] <- NA
nfl_actualStats_seasonal_team_inclPost[sapply(nfl_actualStats_seasonal_team_inclPost, is.infinite)] <- NA
```
